Analysis

### 2019-12-12 analysis.Rmd
arregle un titulo
arregle un titulo

table_ed_gapper <-  ggplot(data=table_ed_gapper, aes(x=reorder(as.factor(years),-median), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Brecha percibida segun Nivel educativo (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
    coord_flip()
table_ed_gapper

@@

table_ed_gapjus <-  ggplot(data=table_ed_gapjus, aes(x=reorder(as.factor(years),-median), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Brecha percibida segun Nivel educativo (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
    coord_flip()
table_ed_gapjus

>>>>

table_ed_gapper <-  ggplot(data=table_ed_gapper, aes(x=reorder(as.factor(years),-median), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Brecha percibida segun nivel educativo (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
    coord_flip()
table_ed_gapper

@@

table_ed_gapjus <-  ggplot(data=table_ed_gapjus, aes(x=reorder(as.factor(years),-median), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Brecha justa segun nivel educativo (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
    coord_flip()
table_ed_gapjus
